Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-12 eswc-2012/phdsymp.tex
value for new users and devs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@175 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

Ultimately, this approach may be of great value to new users of SPARQL
engines, as it can point out key differences between engines and
therefore help users identify aspects that they should investigate
with respect to their own expected uses. By normalizing weights
between features, we may also attempt to advice those who do not know
anything about their expected usage. Similarly, it may of great use to
developers as it would quantify any adverse effects a modification may
have.
